On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-07 AvdMomZvol_rails/Article.tex
[AMZr] Add reference for pyramid sets
[AMZr] Complete the example of a scissors set

%TODO: can a scissors set have another axis of symmetry?

>>>>

Examples of pyramid sets are given in Section~\ref{sec:bounds_pyramid} on
Fig.~\ref{picture_56.png} and Fig.~\ref{picture_1260.png}.
We don't have any examples of pyramid sets with cardinality more than 9.

It still remain unknown whether a scissors set can have another axis of symmetry;
on Fig.~\ref{15_3364_91_30e991f82a54fb9caeca5b6a6776b981_X.png} the following scissors set with central symmetry is shown:
\begin{multline*}
	\sqrt{91}/1*\{
	( 0 ; 0);
	( 792 ; 120);
	( -792 ; -120);
\\
	( \pm256 ; 0);
	( \pm646 ; 0);
	( \pm693 ; 0);
	( \pm1152 ; 0);
	( \pm1242 ; 0);
	( \pm1682 ; 0)
\}
\end{multline*}
